---
title: "report"
author: "AlexCH"
date: "4/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tapestri.tools)
library(patchwork)
library(viridis)
library(umap)
library(ggsci)
library(ggtext)


#read .h5 files
h5f_a <- read_h5("h5_files/mPDX_ID_A.dna+protein.h5")
h5f_b <- read_h5("h5_files/mPDX_ID_B.dna+protein.h5")
h5f_c <- read_h5("h5_files/mpdxC-10_MB_90.dna+protein.h5")
h5f_d <- read_h5("h5_files/mpdxD-18_MB_33_38.dna+protein.h5")
```

#### important variant ids:
(1) chr2:209113112:C/T (IDH1 R132H)
(2) chr15:90631934:C/T (IDH2 R140Q)
(3) chr15:90631838:C/T (IDH2 R172K)
```{r}
int.var <- c(IDH1.R132H = "chr2:209113112:C/T", 
             IDH1.R132C = "chr2:209113113:G/A", #PM325267
             IDH2.R140Q = "chr15:90631934:C/T",
             IDH2.R172K = "chr15:90631838:C/T",
             TP53 = "chr17:7577517:A/C",
             NPM1c = "chr5:170837543:C/CTCTG"
             )
```


# (1) Cell indexing based on sample of origin

## Index for mPDX-B
```{r}
indx_160345 <- get_cells_index(h5f_b, variants = int.var["IDH1.R132H"], c(1, 2))
indx_160345 <- indx_160345[indx_160345 %in% get_cells_index(h5f_b, variants = int.var["IDH1.R132C"], c(0, 3))]

indx_325267 <- get_cells_index(h5f_b, variants = int.var["IDH1.R132C"], c(1, 2))
indx_325267 <- indx_325267[indx_325267 %in% get_cells_index(h5f_b, variants = int.var["IDH1.R132H"], c(0, 3))]

indx_cells_B <- list(PM160345 = indx_160345, PM352567 = indx_325267)
rm(list = c("indx_160345", "indx_325267"))
```

## Index for mPDX-C
```{r}
indx_160345 <- get_cells_index(h5f_c, variants = int.var["IDH1.R132H"], c(1, 2))
indx_160345 <- indx_160345[indx_160345 %in% get_cells_index(h5f_c, variants = int.var["TP53"], c(0, 3))]

indx_150437 <- get_cells_index(h5f_c, variants = int.var["TP53"], c(1, 2))
indx_150437 <- indx_150437[indx_150437 %in% get_cells_index(h5f_c, variants = int.var["IDH1.R132H"], c(0, 3))]

indx_cells_C <- list(PM160345 = indx_160345, PM150437 = indx_150437)
rm(list = c("indx_160345", "indx_150437"))
```

## Index for mPDX-D
```{r}
##
indx_160345 <- get_cells_index(h5f_d, variants = int.var["IDH1.R132H"], c(1, 2))
indx_160345 <- indx_160345[indx_160345 %in% get_cells_index(h5f_d, variants = int.var["IDH2.R140Q"], c(0, 3))]

indx_160053 <- get_cells_index(h5f_d, variants = int.var["IDH2.R140Q"], c(1, 2))
indx_160053 <- indx_160053[indx_160053 %in% get_cells_index(h5f_d, variants = int.var["IDH1.R132H"], c(0, 3))]

indx_cells_D <- list(PM160345 = indx_160345, PM160053 = indx_160053)
rm(list = c("indx_160345", "indx_160053"))
```


# (2) Upset plots to visualize the number of doublets

## Doublets mPDX-B
```{r}
svg("upset_B.svg", width = 3.9, height = 2.67)
plot_upset_with_variants(h5f_b, variants = int.var[c("IDH1.R132H", "IDH1.R132C")])
dev.off()
```

## Doublets mPDX-C
```{r}
svg("upset_C.svg", width = 3.9, height = 2.67)
plot_upset_with_variants(h5f_c, variants = int.var[c("IDH1.R132H", "TP53")])
dev.off()
```

## Doublets mPDX-D
```{r}
svg("upset_D.svg", width = 3.9, height = 2.67)
plot_upset_with_variants(h5f_d, variants = int.var[c("IDH1.R132H", "IDH2.R140Q")])
dev.off()
```

# (3) VAF boxplot in singlets and doublets

## VAF boxplot: mPDX-C
```{r}
read_assays_variants(h5f_c, c("AF", "DP"),
                     index_variants = get_variants_index(h5f_c, variants = int.var[c("IDH1.R132H", "TP53")])
                     )  -> af_dp_C 
#
rownames(af_dp_C$AF) <- paste0("AF_", rownames(af_dp_C$AF))
rownames(af_dp_C$DP) <- paste0("DP_", rownames(af_dp_C$DP))

af_dp_C <- do.call(rbind, af_dp_C) %>% t() %>% as.data.frame()

af_dp_C$sample <- NA
af_dp_C[indx_cells_C$PM160345, "sample"] <- "PM160345"
af_dp_C[indx_cells_C$PM150437, "sample"] <- "PM150437"
af_dp_C[is.na(af_dp_C$sample), "sample"] <- "Multiplet"

af_dp_C$sample <- factor(af_dp_C$sample, levels = c("PM160345", "PM150437", "Multiplet"))
#

ggplot(af_dp_C, aes(sample, AF_IDH1.R132H)) +
  geom_boxplot() +
  labs(x = "Inferred sample of origin", y = "*IDH1*<sup>R132H</sup> allele frequency (%)") +
  theme_minimal(13) +
  theme(axis.title.y = element_markdown()) -> p_AF.IDH1R132H

ggplot(af_dp_C, aes(sample, AF_TP53)) +
  geom_boxplot() +
  labs(x = "Inferred sample of origin", y = "*TP53*<sup>I255S</sup> allele frequency (%)") +
  theme_minimal(13) +
  theme(axis.title.y = element_markdown()) -> p_AF.TP53I255S

p_AF.C <- p_AF.IDH1R132H + p_AF.TP53I255S
#ggsave("plots/AF/p_AF.C.png", p_AF.C, height = 3, width = 7, units = "in", dpi = "retina")

rm(list = c("p_AF.IDH1R132H", "p_AF.TP53I255S"))
```

## VAF boxplot: mPDX-D
```{r}
read_assays_variants(h5f_d, c("AF", "DP"),
                     index_variants = get_variants_index(h5f_d, variants = int.var[c("IDH1.R132H", "IDH2.R140Q")])
                     )  -> af_dp_D
#
rownames(af_dp_D$AF) <- paste0("AF_", rownames(af_dp_D$AF))
rownames(af_dp_D$DP) <- paste0("DP_", rownames(af_dp_D$DP))

af_dp_D <- do.call(rbind, af_dp_D) %>% t() %>% as.data.frame()

af_dp_D$sample <- NA
af_dp_D[indx_cells_D$PM160345, "sample"] <- "PM160345"
af_dp_D[indx_cells_D$PM160053, "sample"] <- "PM160053"
af_dp_D[is.na(af_dp_D$sample), "sample"] <- "Multiplet"

af_dp_D$sample <- factor(af_dp_D$sample, levels = c("PM160345", "PM160053", "Multiplet"))
#

ggplot(af_dp_D, aes(sample, AF_IDH1.R132H)) +
  geom_boxplot() +
  labs(x = "Inferred sample of origin", y = "*IDH1*<sup>R132H</sup> allele frequency (%)") +
  theme_minimal(13) +
  theme(axis.title.y = element_markdown()) -> p_AF.IDH1R132H

ggplot(af_dp_D, aes(sample, AF_IDH2.R140Q)) +
  geom_boxplot() +
  labs(x = "Inferred sample of origin", y = "*IDH2*<sup>R140Q</sup> allele frequency (%)") +
  theme_minimal(13) +
  theme(axis.title.y = element_markdown()) -> p_AF.IDH2R140Q

p_AF.D <- p_AF.IDH1R132H + p_AF.IDH2R140Q
#ggsave("plots/AF/p_AF.D.png", p_AF.D, height = 3, width = 7, units = "in", dpi = "retina")

rm(list = c("p_AF.IDH1R132H", "p_AF.IDH2R140Q"))
```



# (4) Annotate variant with ENSEMBL VEP

## Write input for mPDX-C
```{r}
dt.var_c <- get_variants(h5f_c) %>% subset(filtered == "00") 
#retrieve FLT3-ITD
dt.var_c <- rbind(dt.var_c, subset(get_flt3itd(h5f_c), filtered == "01"))
#write vep input
write_vep_input(dt.var_c, "VEP/input/VEP_input_C.txt")
```

## Write input for mPDX-D
```{r}
dt.var_d <- get_variants(h5f_d) %>% subset(filtered == "00") 
#retrieve FLT3-ITD
dt.var_d <- rbind(dt.var_d, subset(get_flt3itd(h5f_d), filtered == "01"))
##write vep input
#write_vep_input(dt.var_d, "VEP/input/VEP_input_D.txt")
```


## Read VEP output / Write scite input for mPDX-C
```{r}
vep_c <- read_vep_output("VEP/output/VEP_output_C.txt")

vep_c %>% 
  subset(Protein_position != "-") %>% 
  subset(Consequence %in% c("missense_variant", "frameshift_variant", "downstream_gene_variant")) %>% 
  .[!duplicated(.$X.Uploaded_variation), ] %>% 
  dplyr::select(X.Uploaded_variation, Location, Allele, Gene, Feature, Consequence, ends_with("position"), Amino_acids, SYMBOL, SIFT, PolyPhen, EXON) -> vep_c

#remove KIT because it's benign/tolerated
#remove EZH2 because it was not detected in targeted sequencing
vep_c <- subset(vep_c, !grepl("tolerated", SIFT))
vep_c <- subset(vep_c, SYMBOL != "EZH2")

scite_C <- data.frame(
  SYMBOL = c("DNMT3A", "IDH1", "GATA2", "TET2", "TP53", "NPM1"),
  Variant = c("R882C", "R132H", "A372V", "C1709R", "I255S", "NPM1c"),
  id = c(vep_c$X.Uploaded_variation %>% str_split("_") %>% lapply(function(x){x[2]}) %>% unlist(), "chr5:170837543:C/CTCTG")
)
```

## Read VEP output: mPDX-D
```{r}
vep_d <- read_vep_output("VEP/output/VEP_output_D.txt")

vep_d %>% 
  subset(Protein_position != "-") %>% 
  subset(Consequence %in% c("missense_variant", "frameshift_variant", "downstream_gene_variant")) %>% 
  .[!duplicated(.$X.Uploaded_variation), ] %>% 
  dplyr::select(X.Uploaded_variation, Location, Allele, Gene, Feature, Consequence, ends_with("position"), Amino_acids, SYMBOL, SIFT, PolyPhen, EXON) -> vep_d

#remove EZH2 and IDH2 frameshift mutations because they're not detected in targeted sequencing
vep_d <- subset(vep_d, SIFT != "-")


scite_D <- data.frame(
  SYMBOL = c("DNMT3A", "IDH1", "GATA2", "TET2", "TET2", "IDH2", "NPM1", "FLT3"),
  Variant = c("DNMT3A_R882C", "IDH1_R132H", "GATA2_A372V", "TET2_C1709R", "TET2_H1778R", "IDH2_R140Q", "NPM1c", "FLT3_ITD"),
  id = c(vep_d$X.Uploaded_variation %>% str_split("_") %>% lapply(function(x){x[2]}) %>% unlist(), "chr5:170837543:C/CTCTG", "chr13:28608262:T/TTCATATTCTCTGAAATCAACG")
)
scite_D <- scite_D[c(2, 6, 1, 3, 4, 5, 7, 8), ]
rownames(scite_D) <- NULL
```

## Investigate (upset plots) variants from vep: mPDX-D
```{r}
svg("plots/upset/upset_D_filtered_variants.svg", height = 4.3, width = 7.2)
plot_upset_with_variants(h5f_d, 
                         variants = set_names(scite_D$id, scite_D$Variant), 
                         index_cell = c(indx_cells_D$PM160345, indx_cells_D$PM160053),
                         nset = nrow(scite_D))
dev.off()


#DNMT3A-R882C is associated with PM160345
svg("plots/upset/upset_D_DNMT3A-R882C_vs_IDH12.svg", height = 2.8, width = 3.5)
plot_upset_with_variants(h5f_d, 
                         variants = set_names(scite_D$id[c(1, 2, 3)], scite_D$Variant[c(1, 2, 3)]), 
                         index_cell = c(indx_cells_D$PM160345, indx_cells_D$PM160053),
                         nset = nrow(scite_D))
dev.off()

#GATA2-A372V is associated with PM160345
svg("plots/upset/upset_D_GATA2-A372V_vs_IDH12.svg", height = 2.8, width = 3.5)
plot_upset_with_variants(h5f_d, 
                         variants = set_names(scite_D$id[c(1, 2, 4)], scite_D$Variant[c(1, 2, 4)]), 
                         index_cell = c(indx_cells_D$PM160345, indx_cells_D$PM160053),
                         nset = nrow(scite_D))
dev.off()

#TET2-C1709R is associated with PM160345
svg("plots/upset/upset_D_TET2-C1709R_vs_IDH12.svg", height = 2.8, width = 3.5)
plot_upset_with_variants(h5f_d, 
                         variants = set_names(scite_D$id[c(1, 2, 5)], scite_D$Variant[c(1, 2, 5)]), 
                         index_cell = c(indx_cells_D$PM160345, indx_cells_D$PM160053),
                         nset = nrow(scite_D))
dev.off()


#TET2-H1778R is associated with PM160345
svg("plots/upset/upset_D_TET2-H1778R_vs_IDH12.svg", height = 2.8, width = 3.5)
plot_upset_with_variants(h5f_d, 
                         variants = set_names(scite_D$id[c(1, 2, 6)], scite_D$Variant[c(1, 2, 6)]), 
                         index_cell = c(indx_cells_D$PM160345, indx_cells_D$PM160053),
                         nset = nrow(scite_D))
dev.off()

#NPM1c is associated with both PM160345 and PM160053
svg("plots/upset/upset_D_NPM1c_vs_IDH12.svg", height = 2.8, width = 3.5)
plot_upset_with_variants(h5f_d, 
                         variants = set_names(scite_D$id[c(1, 2, 7)], scite_D$Variant[c(1, 2, 7)]), 
                         index_cell = c(indx_cells_D$PM160345, indx_cells_D$PM160053),
                         nset = nrow(scite_D))
dev.off()

#FLT3-ITD is associated with PM160053
svg("plots/upset/upset_D_FLT3-ITD_vs_IDH12.svg", height = 2.8, width = 3.5)
plot_upset_with_variants(h5f_d, 
                         variants = set_names(scite_D$id[c(1, 2, 8)], scite_D$Variant[c(1, 2, 8)]), 
                         index_cell = c(indx_cells_D$PM160345, indx_cells_D$PM160053),
                         nset = nrow(scite_D))
dev.off()
```

## Write scite input: mPDX-D
```{r}
scite_D$PM160345 <- c(1, 0, 1, 1, 1, 0, 1, 0)
scite_D$PM160053 <- c(0, 1, 0, 0, 0, 1, 1, 1)
##write for PM160345: 5 variants across 2919 cells
# x <- scite_D %>% subset(PM160345 == 1)
# x <- set_names(x$id, x$Variant)
# write_scite_inputs(h5f_d,
#                    variants = x,
#                    cell_index = indx_cells_D$PM160345,
#                    fp_ngt_csv = "scite/input/D_PM160345_ngt.csv",
#                    fp_geneNames = "scite/input/D_PM160345.geneNames"
#                    )
# rm(x)

##write for PM160053: 4 variants across 839 cells
# x <- scite_D %>% subset(PM160053 == 1)
# x <- set_names(x$id, x$Variant)
# write_scite_inputs(h5f_d,
#                    variants = x,
#                    cell_index = indx_cells_D$PM160053,
#                    fp_ngt_csv = "scite/input/D_PM160053_ngt.csv",
#                    fp_geneNames = "scite/input/D_PM160053.geneNames"
#                    )
# rm(x)
```

## Read scite output: mPDX-D
```{r}
scite_D_160345 <- read_scite_output("scite/output/D_PM160345_ngt_ml0.gv", cell_index_h5f = indx_cells_D$PM160345)
scite_D_160053 <- read_scite_output("scite/output/D_PM160053_ngt_ml0.gv", cell_index_h5f = indx_cells_D$PM160053)

scite_out_D <- rbind(scite_D_160345, scite_D_160053)
```

# Protein UMAP

## UMAP wrangle: mPDX-C
```{r}
protein_C <- read_protein_counts(h5f_c, normalization = "clr") %>% data.table()
protein_C$index_cell <- 1:nrow(protein_C)
protein_C$NGT_NPM1c <- read_assays_variants(h5f_c, "NGT", index_variants = get_variants_index(h5f_c, int.var["NPM1c"])) %>% unlist()
protein_C <- protein_C %>% subset(index_cell %in% unlist(indx_cells_C))
protein_C$sample <- ifelse(protein_C$index_cell %in% indx_cells_C$PM160345, "PM160345", "PM150437")

umap_C <- umap(dplyr::select(protein_C, starts_with("CD")))
protein_C$umap1 <- umap_C$layout[, 1]
protein_C$umap2 <- umap_C$layout[, 2]
```

## UMAP wrangle: mPDX-D
```{r}
#read and normalize protein counts
protein_D <- read_protein_counts(h5f_d, normalization = "clr") %>% data.table()

#filter out doublets
protein_D$cell_index <- 1:nrow(protein_D)
protein_D <- protein_D %>% subset(cell_index %in% unlist(indx_cells_D))
protein_D$sample <- ifelse(protein_D$cell_index %in% indx_cells_D$PM160345, "PM160345", "PM160053")

#umap
umap_D <- umap(dplyr::select(protein_D, starts_with("CD")))
protein_D$umap1 <- umap_D$layout[, 1]
protein_D$umap2 <- umap_D$layout[, 2]

#combine clonal data
protein_D <- left_join(protein_D, scite_out_D, by = "cell_index")
```

## Individual clone size: mPDX-D
```{r}
clone_size_D <- protein_D %>% group_by(sample, Clone) %>% dplyr::summarise(n = n())
#write_csv(clone_size_D, "clone_size/clone_size_D.csv")
clone_size_D
```

## Clustering: mPDX-D
```{r}
library(factoextra)
# set.seed(69)
# gapStat_D <- clusGap(dplyr::select(protein_D, starts_with("CD")), FUN = kmeans, nstart = 30, K.max = 10, B = 50)

# fviz_gap_stat(gapStat_D) + 
#   ggtitle(NULL) +
#   theme_minimal(13) -> p_protein_cluster_gapstat_D

#ggsave("plots/kmeans_gapstat/p_protein_cluster_gapstat_D.png", plot = p_protein_cluster_gapstat_D, width = 3.5, height = 3, units = "in", dpi = "retina")

km_D <- kmeans(dplyr::select(protein_D, starts_with("CD")), centers = 9, nstart = 30)
protein_D$km_clust <- as.character(km_D$cluster)
```

## Basic UMAP plot: mPDX-D
```{r}
ggplot(protein_D, aes(umap1, umap2, color = sample)) +
    geom_point() +
    scale_color_viridis_d(name = "Sample") +
    theme_void(15) +
    theme(legend.position = "top") -> p_umap_d_sample

ggplot(protein_D, aes(umap1, umap2, color = km_clust)) +
  geom_point() +
  scale_color_npg(name = "Kmeans Cluster") +
  theme_void(15) +
  theme(legend.position = "top") -> p_umap_d_km

p.umap.d <- p_umap_d_sample + p_umap_d_km
#ggsave("plots/umap/p_umap.d.png", plot = p.umap.d, height = 3.5, width = 9, dpi = "retina", units = "in")

```



## Wrapped UMAP plot: mPDX-C
```{r}
#facet by protein 
ls_umap_c <- list()
for(i in get_protein_ids(h5f_c)){
  ggplot(protein_C, aes_string("umap1", "umap2", color = i)) + 
    geom_point() + 
    theme_classic() + 
    labs(x = "UMAP1", y = "UMAP2") +
    scale_color_viridis_c() -> p
  
  ls_umap_c[[i]] <- p
}

p.umap.out.C <- patchwork::wrap_plots(ls_umap_c, nrow = 2)
ggsave("protein_umap_C.png", p.umap.out.C, height = 5, width = 15, units = "in", dpi = "retina")
#####

#facet by patient
ggplot(protein_C, aes(umap1, umap2, color = sample)) + 
    geom_point() + 
    theme_classic() + 
    labs(x = "UMAP1", y = "UMAP2") +
    scale_color_viridis_d() -> p.umap.sample.C
ggsave("protein_umap_sample_C.png", p.umap.sample.C, height = 5, width = 5.85, units = "in", dpi = "retina")
#####

#violin
protein_C %>% 
    pivot_longer(starts_with("CD"), names_to = "marker", values_to = "normalized_count") %>% 
    ggplot(aes(sample, normalized_count, fill = sample)) +
    geom_violin() +
    facet_wrap(~marker, scales = "free_y", nrow = 2) +
    scale_fill_viridis_d(guide = "none") +
    labs(x = "Sample", y = "Normalized Count") +
    theme_classic() -> p.violin.c
ggsave("protein_violin_C.png", p.violin.c, height = 5, width = 15, units = "in", dpi = "retina")
```




## Wrapped UMAP plot for legend: mPDX-D
```{r}
#facet by protein 
ls_umap_d <- list()
for(i in get_protein_ids(h5f_d)){
  ggplot(protein_D, aes_string("umap1", "umap2", color = i)) + 
    geom_point() + 
    theme_void(25) + 
    labs(x = "UMAP1", y = "UMAP2") +
    scale_color_viridis_c() -> p
  
  ls_umap_d[[i]] <- p
}

p.umap.out.D <- patchwork::wrap_plots(ls_umap_d, nrow = 2)
ggsave("plots/umap/protein_umap_D.png", p.umap.out.D, height = 5, width = 20, units = "in", dpi = "retina")
```


## Violin plot: mPDX-D
```{r}
#violin
protein_D_long <- protein_D %>% 
  mutate(group = interaction(sample, Clone)) %>% 
  pivot_longer(starts_with("CD"), names_to = "marker", values_to = "normalized_count") 

#reorder group
protein_D_long$group <- factor(protein_D_long$group, levels = c("PM160345.IDH1_R132H",
                                                                "PM160345.DNMT3A_R882C",
                                                                "PM160345.NPM1c",
                                                                "PM160345.GATA2_A372V",
                                                                "PM160345.TET2_C1709R",
                                                                "PM160053.IDH2_R140Q",
                                                                "PM160053.NPM1c",
                                                                "PM160053.TET2_H1778R",
                                                                "PM160053.FLT3_ITD"
                                                                ))

color_clone_D <- data.frame(group = levels(protein_D_long$group),
                            color = ggsci::pal_npg()(10)[1:9]
                            )

protein_D_long$group <- factor(protein_D_long$group, levels = c("PM160345.IDH1_R132H",
                                                                "PM160345.DNMT3A_R882C",
                                                                "PM160345.NPM1c",
                                                                "PM160345.GATA2_A372V",
                                                                "PM160345.TET2_C1709R",
                                                                "PM160053.IDH2_R140Q",
                                                                "PM160053.TET2_H1778R",
                                                                "PM160053.NPM1c",
                                                                "PM160053.FLT3_ITD"
                                                                ) %>% rev())


ggplot(protein_D_long, aes(group, normalized_count, fill = group)) +
    geom_violin() +
    scale_x_discrete(label = c("*IDH1*<sup>R132H</sup>",
                               "*DNMT3A*<sup>R882C</sup>",
                               "*NPM1c*",
                               "*GATA2*<sup>A372V</sup>",
                               "*TET2*<sup>C1709R</sup>",
                               "*IDH2*<sup>R140Q</sup>",
                               "*TET2*<sup>H1778R</sup>",
                               "*NPM1c*",
                               "*FLT3*-ITD"
    ) %>% rev()) +
    facet_grid(~marker, scales = "free_x") +
    scale_fill_manual(values = set_names(color_clone_D$color, color_clone_D$group),
                      guide = "none") +
    labs(x = NULL, y = "Normalized Count") +
    theme_minimal(15) +
    theme(axis.text.y = element_markdown()) +
    coord_flip() -> p_violin_by_clone_D
    
ggsave("plots/violin/p_violin_by_clone_D.png", p_violin_by_clone_D, width = 11.2, height = 4.2, dpi = "retina", units = "in")
```

## contour plots: mPDX-C
```{r}
ggplot(protein_C, aes(CD11b, CD14, color = sample)) + 
    geom_density_2d() +
    scale_color_manual(values = c(PM150437 = "navy", PM160345 = "firebrick")) +
    theme_bw(15) -> p.cd11b.cd14.C
ggsave("cd11b_cd14_C.png", p.cd11b.cd14.C, height = 5, width = 5.85, units = "in", dpi = "retina")
```


